A parallel general purpose multi-objective optimization framework, with application to electron beam dynamics

### 2019-03-25 paper/submission/prab.tex
adding bbl to main tex files

\bibliography{paper}

>>>>

%\bibliography{paper}

%merlin.mbs apsrev4-1.bst 2010-07-25 4.21a (PWD, AO, DPC) hacked
%Control: key (0)
%Control: author (8) initials jnrlst
%Control: editor formatted (1) identically to author
%Control: production of article title (-1) disabled
%Control: page (0) single
%Control: year (1) truncated
%Control: production of eprint (0) enabled
\providecommand{\SortNoop}[1]{}
\begin{thebibliography}{34}%
	\makeatletter
	\providecommand \@ifxundefined [1]{%
		\@ifx{#1\undefined}
	}%
	\providecommand \@ifnum [1]{%
		\ifnum #1\expandafter \@firstoftwo
		\else \expandafter \@secondoftwo
		\fi
	}%
	\providecommand \@ifx [1]{%
		\ifx #1\expandafter \@firstoftwo
		\else \expandafter \@secondoftwo
		\fi
	}%
	\providecommand \natexlab [1]{#1}%
	\providecommand \enquote  [1]{``#1''}%
	\providecommand \bibnamefont  [1]{#1}%
	\providecommand \bibfnamefont [1]{#1}%
	\providecommand \citenamefont [1]{#1}%
	\providecommand \href@noop [0]{\@secondoftwo}%
	\providecommand \href [0]{\begingroup \@sanitize@url \@href}%
	\providecommand \@href[1]{\@@startlink{#1}\@@href}%
	\providecommand \@@href[1]{\endgroup#1\@@endlink}%
	\providecommand \@sanitize@url [0]{\catcode `\\12\catcode `\$12\catcode
		`\&12\catcode `\#12\catcode `\^12\catcode `\_12\catcode `\%12\relax}%
	\providecommand \@@startlink[1]{}%
	\providecommand \@@endlink[0]{}%
	\providecommand \url  [0]{\begingroup\@sanitize@url \@url }%
	\providecommand \@url [1]{\endgroup\@href {#1}{\urlprefix }}%
	\providecommand \urlprefix  [0]{URL }%
	\providecommand \Eprint [0]{\href }%
	\providecommand \doibase [0]{http://dx.doi.org/}%
	\providecommand \selectlanguage [0]{\@gobble}%
	\providecommand \bibinfo  [0]{\@secondoftwo}%
	\providecommand \bibfield  [0]{\@secondoftwo}%
	\providecommand \translation [1]{[#1]}%
	\providecommand \BibitemOpen [0]{}%
	\providecommand \bibitemStop [0]{}%
	\providecommand \bibitemNoStop [0]{.\EOS\space}%
	\providecommand \EOS [0]{\spacefactor3000\relax}%
	\providecommand \BibitemShut  [1]{\csname bibitem#1\endcsname}%
	\let\auto@bib@innerbib\@empty
	%</preamble>
	\bibitem [{\citenamefont {Huang}(2018)}]{xiaobiao}%
	\BibitemOpen
	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {X.}~\bibnamefont
			{Huang}},\ }\href {\doibase 10.1103/PhysRevAccelBeams.21.104601} {\bibfield
		{journal} {\bibinfo  {journal} {Phys. Rev. Accel. Beams}\ }\textbf {\bibinfo
			{volume} {21}},\ \bibinfo {pages} {104601} (\bibinfo {year}
		{2018})}\BibitemShut {NoStop}%
	\bibitem [{\citenamefont {Bazarov}\ and\ \citenamefont
		{Sinclair}(2005)}]{bazarov05}%
	\BibitemOpen
	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {I.~V.}\ \bibnamefont
			{Bazarov}}\ and\ \bibinfo {author} {\bibfnamefont {C.~K.}\ \bibnamefont
			{Sinclair}},\ }\href {\doibase 10.1103/PhysRevSTAB.8.034202} {\bibfield
		{journal} {\bibinfo  {journal} {Phys. Rev. ST Accel. Beams}\ }\textbf
		{\bibinfo {volume} {8}},\ \bibinfo {pages} {034202} (\bibinfo {year}
		{2005})}\BibitemShut {NoStop}%
	\bibitem [{\citenamefont {Yang}\ \emph {et~al.}(2009)\citenamefont {Yang},
		\citenamefont {Robin}, \citenamefont {Sannibale}, \citenamefont {Steier},\
		and\ \citenamefont {Wan}}]{yrss:09}%
	\BibitemOpen
	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
			{Yang}}, \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Robin}},
		\bibinfo {author} {\bibfnamefont {F.}~\bibnamefont {Sannibale}}, \bibinfo
		{author} {\bibfnamefont {C.}~\bibnamefont {Steier}}, \ and\ \bibinfo {author}
		{\bibfnamefont {W.}~\bibnamefont {Wan}},\ }\href {\doibase
		10.1016/j.nima.2009.08.027} {\bibfield  {journal} {\bibinfo  {journal} {Nucl.
				Instrum. Methods Phys. Res. A}\ }\textbf {\bibinfo {volume} {609}},\ \bibinfo
		{pages} {50} (\bibinfo {year} {2009})}\BibitemShut {NoStop}%
	\bibitem [{\citenamefont {Chao}\ \emph {et~al.}(2009)\citenamefont {Chao},
		\citenamefont {Ames}, \citenamefont {Baartman}, \citenamefont {Bylinskii},
		\citenamefont {Dechoudhury}, \citenamefont {Goh}, \citenamefont
		{Koscielniak}, \citenamefont {E~Laxdal}, \citenamefont {Marchetto},
		\citenamefont {Merminga}, \citenamefont {Naik}, \citenamefont {A~Verzilov},
		\citenamefont {Yan},\ and\ \citenamefont {Zvyagintsev}}]{chao09}%
	\BibitemOpen
	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont
			{Chao}}, \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont {Ames}}, \bibinfo
		{author} {\bibfnamefont {R.}~\bibnamefont {Baartman}}, \bibinfo {author}
		{\bibfnamefont {I.}~\bibnamefont {Bylinskii}}, \bibinfo {author}
		{\bibfnamefont {S.}~\bibnamefont {Dechoudhury}}, \bibinfo {author}
		{\bibfnamefont {G.}~\bibnamefont {Goh}}, \bibinfo {author} {\bibfnamefont
			{S.}~\bibnamefont {Koscielniak}}, \bibinfo {author} {\bibfnamefont
			{R.}~\bibnamefont {E~Laxdal}}, \bibinfo {author} {\bibfnamefont
			{M.}~\bibnamefont {Marchetto}}, \bibinfo {author} {\bibfnamefont
			{L.}~\bibnamefont {Merminga}}, \bibinfo {author} {\bibfnamefont
			{V.}~\bibnamefont {Naik}}, \bibinfo {author} {\bibfnamefont {V.}~\bibnamefont
			{A~Verzilov}}, \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont {Yan}}, \
		and\ \bibinfo {author} {\bibfnamefont {V.}~\bibnamefont {Zvyagintsev}},\ }in\
	\href@noop {} {\emph {\bibinfo {booktitle} {Proc. of ICAP}}}\ (\bibinfo
	{year} {2009})\ p.\ \bibinfo {pages} {THPSC012}\BibitemShut {NoStop}%
	\bibitem [{\citenamefont {Gong}\ and\ \citenamefont {Chao}(2012)}]{gong12}%
	\BibitemOpen
	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
			{Gong}}\ and\ \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Chao}},\
	}in\ \href@noop {} {\emph {\bibinfo {booktitle} {Proc. of ICAP}}}\ (\bibinfo
	{year} {2012})\ p.\ \bibinfo {pages} {TUABI1}\BibitemShut {NoStop}%
	\bibitem [{\citenamefont {Hofler}\ \emph {et~al.}(2013)\citenamefont {Hofler},
		\citenamefont {Terzic}, \citenamefont {Kramer}, \citenamefont {Zvezdin},
		\citenamefont {Morozov}, \citenamefont {Roblin}, \citenamefont {Lin},\ and\
		\citenamefont {Jarvis}}]{hofler13}%
	\BibitemOpen
	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
			{Hofler}}, \bibinfo {author} {\bibfnamefont {B.}~\bibnamefont {Terzic}},
		\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Kramer}}, \bibinfo
		{author} {\bibfnamefont {A.}~\bibnamefont {Zvezdin}}, \bibinfo {author}
		{\bibfnamefont {V.}~\bibnamefont {Morozov}}, \bibinfo {author} {\bibfnamefont
			{Y.}~\bibnamefont {Roblin}}, \bibinfo {author} {\bibfnamefont
			{F.}~\bibnamefont {Lin}}, \ and\ \bibinfo {author} {\bibfnamefont
			{C.}~\bibnamefont {Jarvis}},\ }\href {\doibase 10.1103/PhysRevSTAB.16.010101}
	{\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. ST Accel. Beams}\
		}\textbf {\bibinfo {volume} {16}},\ \bibinfo {pages} {010101} (\bibinfo
		{year} {2013})}\BibitemShut {NoStop}%
	%%CITATION = PRSTA,16,010101;%%
	\bibitem [{\citenamefont {Terzic}\ \emph {et~al.}(2014)\citenamefont {Terzic},
		\citenamefont {Hofler}, \citenamefont {Reeves}, \citenamefont {Khan},
		\citenamefont {Krafft}, \citenamefont {Benesch}, \citenamefont {Freyberger},\
		and\ \citenamefont {Ranjan}}]{jefferson}%
	\BibitemOpen
	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {B.}~\bibnamefont
			{Terzic}}, \bibinfo {author} {\bibfnamefont {A.~S.}\ \bibnamefont {Hofler}},
		\bibinfo {author} {\bibfnamefont {C.~J.}\ \bibnamefont {Reeves}}, \bibinfo
		{author} {\bibfnamefont {S.~A.}\ \bibnamefont {Khan}}, \bibinfo {author}
		{\bibfnamefont {G.~A.}\ \bibnamefont {Krafft}}, \bibinfo {author}
		{\bibfnamefont {J.}~\bibnamefont {Benesch}}, \bibinfo {author} {\bibfnamefont
			{A.}~\bibnamefont {Freyberger}}, \ and\ \bibinfo {author} {\bibfnamefont
			{D.}~\bibnamefont {Ranjan}},\ }\href {\doibase 10.1103/PhysRevSTAB.17.101003}
	{\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. ST Accel. Beams}\
		}\textbf {\bibinfo {volume} {17}},\ \bibinfo {pages} {101003} (\bibinfo
		{year} {2014})}\BibitemShut {NoStop}%
	\bibitem [{\citenamefont {Gong}\ and\ \citenamefont {Chao}(2015)}]{gong15}%
	\BibitemOpen
	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
			{Gong}}\ and\ \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Chao}},\
	}in\ \href@noop {} {\emph {\bibinfo {booktitle} {Proc. of ICAP}}}\ (\bibinfo
	{year} {2015})\ p.\ \bibinfo {pages} {THCWC4}\BibitemShut {NoStop}%
	\bibitem [{\citenamefont {Gong}(2015)}]{gongthesis15}%
	\BibitemOpen
	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
			{Gong}},\ }\emph {\bibinfo {title} {A Novel Optimization Platform and Its
			Applications to the TRIUMF Energy Recovery Linac}},\ \href@noop {} {Ph.D.
		thesis},\ \bibinfo  {school} {The University of Columbia} (\bibinfo {year}
	{2015})\BibitemShut {NoStop}%
	\bibitem [{\citenamefont {Gulliford}\ \emph {et~al.}(2016)\citenamefont
		{Gulliford}, \citenamefont {Bartnik},\ and\ \citenamefont {Bazarov}}]{gull1}%
	\BibitemOpen
	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
			{Gulliford}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Bartnik}},
		\ and\ \bibinfo {author} {\bibfnamefont {I.}~\bibnamefont {Bazarov}},\ }\href
	{\doibase 10.1103/PhysRevAccelBeams.19.093402} {\bibfield  {journal}
		{\bibinfo  {journal} {Phys. Rev. Accel. Beams}\ }\textbf {\bibinfo {volume}
			{19}},\ \bibinfo {pages} {093402} (\bibinfo {year} {2016})}\BibitemShut
	{NoStop}%
	\bibitem [{\citenamefont {Gulliford}\ \emph {et~al.}(2017)\citenamefont
		{Gulliford}, \citenamefont {Bartnik}, \citenamefont {Bazarov},\ and\
		\citenamefont {Maxson}}]{gull2}%
	\BibitemOpen
	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
			{Gulliford}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Bartnik}},
		\bibinfo {author} {\bibfnamefont {I.}~\bibnamefont {Bazarov}}, \ and\
		\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Maxson}},\ }\href
	{\doibase 10.1103/PhysRevAccelBeams.20.033401} {\bibfield  {journal}
		{\bibinfo  {journal} {Phys. Rev. Accel. Beams}\ }\textbf {\bibinfo {volume}
			{20}},\ \bibinfo {pages} {033401} (\bibinfo {year} {2017})}\BibitemShut
	{NoStop}%
	\bibitem [{\citenamefont {Kranjčević}\ \emph {et~al.}(2019)\citenamefont
		{Kranjčević}, \citenamefont {Adelmann}, \citenamefont {Arbenz},
		\citenamefont {Citterio},\ and\ \citenamefont {Stingelin}}]{marija}%
	\BibitemOpen
	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
			{Kranjčević}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
			{Adelmann}}, \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Arbenz}},
		\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Citterio}}, \ and\
		\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Stingelin}},\ }\href
	{\doibase https://doi.org/10.1016/j.nima.2018.12.066} {\bibfield  {journal}
		{\bibinfo  {journal} {Nucl. Instrum. Methods Phys. Res. A}\ }\textbf
		{\bibinfo {volume} {920}},\ \bibinfo {pages} {106 } (\bibinfo {year}
		{2019})}\BibitemShut {NoStop}%
	\bibitem [{\citenamefont {Physics}(2018)}]{gpt}%
	\BibitemOpen
	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
			{Physics}},\ }\href@noop {} {\enquote {\bibinfo {title} {{General Particle
					Tracer (GPT)}},}\ } (\bibinfo {year} {1996-2018}),\ \Eprint
	{http://arxiv.org/abs/\url{http://www.pulsar.nl/gpt}}
	{\url{http://www.pulsar.nl/gpt}} \BibitemShut {NoStop}%
	\bibitem [{\citenamefont {Borland}(2018)}]{elegant}%
	\BibitemOpen
	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
			{Borland}},\ }\href@noop {} {\emph {\bibinfo {title} {Elegant: A flexible
				SDDS-compliant code for accelerator simulation}}},\ \bibinfo {type} {Tech.
		Rep.}\ \bibinfo {number} {LS-287}\ (\bibinfo  {institution} {Argonne National
		Laboratory},\ \bibinfo {year} {2000-2018})\BibitemShut {NoStop}%
	\bibitem [{\citenamefont {Adelmann}\ \emph {et~al.}(2018)\citenamefont
		{Adelmann}, \citenamefont {Baumgarten}, \citenamefont {Frey}, \citenamefont
		{Gsell}, \citenamefont {Rizzoglio}, \citenamefont {Snuverink}, \citenamefont
		{Metzger-Kraus}, \citenamefont {Ineichen}, \citenamefont {Russell},
		\citenamefont {Wang}, \citenamefont {Sheehy}, \citenamefont {Rogers},\ and\
		\citenamefont {Winklehner}}]{opal}%
	\BibitemOpen
	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
			{Adelmann}}, \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
			{Baumgarten}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Frey}},
		\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Gsell}}, \bibinfo
		{author} {\bibfnamefont {V.}~\bibnamefont {Rizzoglio}}, \bibinfo {author}
		{\bibfnamefont {J.}~\bibnamefont {Snuverink}}, \bibinfo {author}
		{\bibfnamefont {C.}~\bibnamefont {Metzger-Kraus}}, \bibinfo {author}
		{\bibfnamefont {Y.}~\bibnamefont {Ineichen}}, \bibinfo {author}
		{\bibfnamefont {S.}~\bibnamefont {Russell}}, \bibinfo {author} {\bibfnamefont
			{C.}~\bibnamefont {Wang}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
			{Sheehy}}, \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {Rogers}}, \
		and\ \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Winklehner}},\
	}\href@noop {} {\emph {\bibinfo {title} {The {OPAL} (Object Oriented Parallel
				Accelerator Library) Framework}}},\ \bibinfo {type} {Tech. Rep.}\ \bibinfo
	{number} {PSI-PR-08-02}\ (\bibinfo  {institution} {Paul Scherrer Institut},\
	\bibinfo {year} {2008-2018})\BibitemShut {NoStop}%
	\bibitem [{\citenamefont {Deb}\ \emph {et~al.}(2002)\citenamefont {Deb},
		\citenamefont {Pratap}, \citenamefont {Agarwal},\ and\ \citenamefont
		{Meyarivan}}]{dpam:02}%
	\BibitemOpen
	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {K.}~\bibnamefont
			{Deb}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Pratap}},
		\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Agarwal}}, \ and\
		\bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Meyarivan}},\ }\href
	{\doibase 10.1109/4235.996017} {\bibfield  {journal} {\bibinfo  {journal}
			{IEEE Trans. Evol. Comp.}\ }\textbf {\bibinfo {volume} {6}},\ \bibinfo
		{pages} {182} (\bibinfo {year} {2002})}\BibitemShut {NoStop}%
	\bibitem [{\citenamefont {Bleuler}\ \emph {et~al.}(2003)\citenamefont
		{Bleuler}, \citenamefont {Laumanns}, \citenamefont {Thiele},\ and\
		\citenamefont {Zitzler}}]{pisa}%
	\BibitemOpen
	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
			{Bleuler}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Laumanns}},
		\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Thiele}}, \ and\ \bibinfo
		{author} {\bibfnamefont {E.}~\bibnamefont {Zitzler}},\ }in\ \href@noop {}
	{\emph {\bibinfo {booktitle} {{E}volutionary {M}ulti-{C}riterion
				{O}ptimization}}},\ \bibinfo {editor} {edited by\ \bibinfo {editor}
		{\bibfnamefont {C.~M.}\ \bibnamefont {Fonseca}}, \bibinfo {editor}
		{\bibfnamefont {P.~J.}\ \bibnamefont {Fleming}}, \bibinfo {editor}
		{\bibfnamefont {E.}~\bibnamefont {Zitzler}}, \bibinfo {editor} {\bibfnamefont
			{L.}~\bibnamefont {Thiele}}, \ and\ \bibinfo {editor} {\bibfnamefont
			{K.}~\bibnamefont {Deb}}}\ (\bibinfo  {publisher} {Springer},\ \bibinfo
	{address} {Berlin, Heidelberg},\ \bibinfo {year} {2003})\ pp.\ \bibinfo
	{pages} {494--508}\BibitemShut {NoStop}%
	\bibitem [{\citenamefont {Deb}(2009)}]{deb:09}%
	\BibitemOpen
	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {K.}~\bibnamefont
			{Deb}},\ }\href@noop {} {\emph {\bibinfo {title} {{M}ulti-{O}bjective
				{O}ptimization {U}sing {E}volutionary {A}lgorithms}}}\ (\bibinfo  {publisher}
	{Wiley},\ \bibinfo {year} {2009})\BibitemShut {NoStop}%
	\bibitem [{\citenamefont {Kirkpatrick}\ \emph {et~al.}(1983)\citenamefont
		{Kirkpatrick}, \citenamefont {Gelatt},\ and\ \citenamefont
		{Vecchi}}]{kigv:83}%
	\BibitemOpen
	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
			{Kirkpatrick}}, \bibinfo {author} {\bibfnamefont {C.~D.}\ \bibnamefont
			{Gelatt}}, \ and\ \bibinfo {author} {\bibfnamefont {M.~P.}\ \bibnamefont
			{Vecchi}},\ }\href {\doibase 10.1126/science.220.4598.671} {\bibfield
		{journal} {\bibinfo  {journal} {Science}\ }\textbf {\bibinfo {volume}
			{220}},\ \bibinfo {pages} {671} (\bibinfo {year} {1983})}\BibitemShut
	{NoStop}%
	\bibitem [{\citenamefont {Kennedy}\ and\ \citenamefont
		{Eberhart}(1995)}]{keeb:95}%
	\BibitemOpen
	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
			{Kennedy}}\ and\ \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont
			{Eberhart}},\ }in\ \href {\doibase 10.1109/ICNN.1995.488968} {\emph {\bibinfo
			{booktitle} {Proc. of ICNN}}},\ Vol.~\bibinfo {volume} {4}\ (\bibinfo {year}
	{1995})\ pp.\ \bibinfo {pages} {1942--1948}\BibitemShut {NoStop}%
	\bibitem [{\citenamefont {Dorigo}\ \emph {et~al.}(1996)\citenamefont {Dorigo},
		\citenamefont {Maniezzo},\ and\ \citenamefont {Colorni}}]{domc:96}%
	\BibitemOpen
	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
			{Dorigo}}, \bibinfo {author} {\bibfnamefont {V.}~\bibnamefont {Maniezzo}}, \
		and\ \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Colorni}},\
	}\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {IEEE Trans. Syst.
				Man. Cy. B}\ }\textbf {\bibinfo {volume} {26}},\ \bibinfo {pages} {29}
		(\bibinfo {year} {1996})}\BibitemShut {NoStop}%
	\bibitem [{\citenamefont {De~Castro}\ and\ \citenamefont
		{Timmis}(2002)}]{cati:02}%
	\BibitemOpen
	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
			{De~Castro}}\ and\ \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
			{Timmis}},\ }\href@noop {} {\emph {\bibinfo {title} {Artificial immune
				systems: a new computational intelligence approach}}}\ (\bibinfo  {publisher}
	{Springer},\ \bibinfo {year} {2002})\BibitemShut {NoStop}%
	\bibitem [{\citenamefont {Karaboga}(2005)}]{kara:05}%
	\BibitemOpen
	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
			{Karaboga}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
			{Techn. Rep. TR06, Erciyes Univ. Press, Erciyes}\ } (\bibinfo {year}
		{2005})}\BibitemShut {NoStop}%
	\bibitem [{\citenamefont {Shah-Hosseini}(2009)}]{hoss:09}%
	\BibitemOpen
	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
			{Shah-Hosseini}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
			{Int. J. Bio-Inspir. Com.}\ }\textbf {\bibinfo {volume} {1}},\ \bibinfo
		{pages} {71} (\bibinfo {year} {2009})}\BibitemShut {NoStop}%
	\bibitem [{\citenamefont {Durillo}\ \emph {et~al.}(2006)\citenamefont
		{Durillo}, \citenamefont {Nebro}, \citenamefont {Luna}, \citenamefont
		{Dorronsoro},\ and\ \citenamefont {Alba}}]{dnld:06}%
	\BibitemOpen
	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
			{Durillo}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Nebro}},
		\bibinfo {author} {\bibfnamefont {F.}~\bibnamefont {Luna}}, \bibinfo {author}
		{\bibfnamefont {B.}~\bibnamefont {Dorronsoro}}, \ and\ \bibinfo {author}
		{\bibfnamefont {E.}~\bibnamefont {Alba}},\ }\href@noop {} {\emph {\bibinfo
			{title} {jMetal: a java framework for developing multi-objective optimization
				metaheuristics}}},\ \bibinfo {type} {Tech. Rep.}\ \bibinfo {number}
	{ITI-2006-10}\ (\bibinfo  {institution} {University of M{\'a}laga, ETSI
		Inform{\'a}tica, Campus de Teatinos},\ \bibinfo {year} {2006})\BibitemShut
	{NoStop}%
	\bibitem [{\citenamefont {Liefooghe}\ \emph {et~al.}(2007)\citenamefont
		{Liefooghe}, \citenamefont {Basseur}, \citenamefont {Jourdan},\ and\
		\citenamefont {Talbi}}]{lbjt:07}%
	\BibitemOpen
	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
			{Liefooghe}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Basseur}},
		\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Jourdan}}, \ and\
		\bibinfo {author} {\bibfnamefont {E.}~\bibnamefont {Talbi}},\ }in\ \href@noop
	{} {\emph {\bibinfo {booktitle} {Evolutionary Multi-Criterion
				Optimization}}}\ (\bibinfo {organization} {Springer},\ \bibinfo {year}
	{2007})\ pp.\ \bibinfo {pages} {386--400}\BibitemShut {NoStop}%
	\bibitem [{\citenamefont {Filipi\v{c}}\ and\ \citenamefont
		{Depolli}(2009)}]{fide:09}%
	\BibitemOpen
	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {B.}~\bibnamefont
			{Filipi\v{c}}}\ and\ \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
			{Depolli}},\ }in\ \href {\doibase 10.1007/978-1-84882-409-6\_7} {\emph
		{\bibinfo {booktitle} {Parallel Computing}}},\ \bibinfo {editor} {edited by\
		\bibinfo {editor} {\bibfnamefont {R.}~\bibnamefont {Trobec}}, \bibinfo
		{editor} {\bibfnamefont {M.}~\bibnamefont {Vajter\v{s}ic}}, \ and\ \bibinfo
		{editor} {\bibfnamefont {P.}~\bibnamefont {Zinterhof}}}\ (\bibinfo
	{publisher} {Springer},\ \bibinfo {year} {2009})\ pp.\ \bibinfo {pages}
	{217--240}\BibitemShut {NoStop}%
	\bibitem [{\citenamefont {Le\'{o}n}\ \emph {et~al.}(2009)\citenamefont
		{Le\'{o}n}, \citenamefont {Miranda},\ and\ \citenamefont {Segura}}]{lems:09}%
	\BibitemOpen
	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
			{Le\'{o}n}}, \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont {Miranda}}, \
		and\ \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {Segura}},\ }\href
	{\doibase 10.1142/S0218213009000275} {\bibfield  {journal} {\bibinfo
			{journal} {Int. J. Artif. Intell. Tools}\ }\textbf {\bibinfo {volume} {18}},\
		\bibinfo {pages} {569} (\bibinfo {year} {2009})}\BibitemShut {NoStop}%
	\bibitem [{\citenamefont {Huband}\ \emph {et~al.}(2005)\citenamefont {Huband},
		\citenamefont {Barone}, \citenamefont {While},\ and\ \citenamefont
		{Hingston}}]{hbwh:05}%
	\BibitemOpen
	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
			{Huband}}, \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Barone}},
		\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {While}}, \ and\ \bibinfo
		{author} {\bibfnamefont {P.}~\bibnamefont {Hingston}},\ }in\ \href {\doibase
		10.1007/978-3-540-31880-4_20} {\emph {\bibinfo {booktitle} {Proc. of Intl.
				Conf. Evol. Multi-Criterion Optimization}}}\ (\bibinfo  {publisher}
	{Springer-Verlag},\ \bibinfo {address} {Berlin, Heidelberg},\ \bibinfo {year}
	{2005})\ pp.\ \bibinfo {pages} {280--295}\BibitemShut {NoStop}%
	\bibitem [{\citenamefont {While}\ \emph {et~al.}(2012)\citenamefont {While},
		\citenamefont {Bradstreet},\ and\ \citenamefont {Barone}}]{whbb:12}%
	\BibitemOpen
	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
			{While}}, \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Bradstreet}}, \
		and\ \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Barone}},\
	}\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {IEEE Trans. Evol.
				Comput.}\ }\textbf {\bibinfo {volume} {16}},\ \bibinfo {pages} {86} (\bibinfo
		{year} {2012})}\BibitemShut {NoStop}%
	\bibitem [{\citenamefont {Gai}\ \emph {et~al.}(2012)\citenamefont {Gai},
		\citenamefont {Power},\ and\ \citenamefont {Jing}}]{gai_power_jing_2012}%
	\BibitemOpen
	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {W.}~\bibnamefont
			{Gai}}, \bibinfo {author} {\bibfnamefont {J.~G.}\ \bibnamefont {Power}}, \
		and\ \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {Jing}},\ }\href
	{\doibase 10.1017/S0022377812000037} {\bibfield  {journal} {\bibinfo
			{journal} {Journal of Plasma Physics}\ }\textbf {\bibinfo {volume} {78}},\
		\bibinfo {pages} {339–345} (\bibinfo {year} {2012})}\BibitemShut {NoStop}%
	\bibitem [{\citenamefont {Jing}\ \emph {et~al.}(2018)\citenamefont {Jing} \emph
		{et~al.}}]{JING201872}%
	\BibitemOpen
	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
			{Jing}} \emph {et~al.},\ }\href {\doibase
		https://doi.org/10.1016/j.nima.2018.05.007} {\bibfield  {journal} {\bibinfo
			{journal} {Nucl. Instrum. Methods Phys. Res. A}\ }\textbf {\bibinfo {volume}
			{898}},\ \bibinfo {pages} {72 } (\bibinfo {year} {2018})}\BibitemShut
	{NoStop}%
	\bibitem [{\citenamefont {Gao}\ \emph {et~al.}(2008)\citenamefont {Gao},
		\citenamefont {Conde}, \citenamefont {Gai}, \citenamefont {Jing},
		\citenamefont {Konecny}, \citenamefont {Liu}, \citenamefont {Power},
		\citenamefont {Wong},\ and\ \citenamefont {Yusof}}]{PETSeq}%
	\BibitemOpen
	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
			{Gao}}, \bibinfo {author} {\bibfnamefont {M.~E.}\ \bibnamefont {Conde}},
		\bibinfo {author} {\bibfnamefont {W.}~\bibnamefont {Gai}}, \bibinfo {author}
		{\bibfnamefont {C.}~\bibnamefont {Jing}}, \bibinfo {author} {\bibfnamefont
			{R.}~\bibnamefont {Konecny}}, \bibinfo {author} {\bibfnamefont
			{W.}~\bibnamefont {Liu}}, \bibinfo {author} {\bibfnamefont {J.~G.}\
			\bibnamefont {Power}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
			{Wong}}, \ and\ \bibinfo {author} {\bibfnamefont {Z.}~\bibnamefont {Yusof}},\
	}\href {\doibase 10.1103/PhysRevSTAB.11.041301} {\bibfield  {journal}
		{\bibinfo  {journal} {Phys. Rev. ST Accel. Beams}\ }\textbf {\bibinfo
			{volume} {11}},\ \bibinfo {pages} {041301} (\bibinfo {year}
		{2008})}\BibitemShut {NoStop}%
	\bibitem [{\citenamefont {Neveu}(2018)}]{neveuthesis}%
	\BibitemOpen
	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.}~\bibnamefont
			{Neveu}},\ }\emph {\bibinfo {title} {Beam Line Design for Fully Staged Two
